Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-17 paper.qmd
Updated the code

axes_obj <- gen_axes(  
  proj = projection * 2,
  limits = 0.5,
  axis_pos_x = -0.5,
  axis_pos_y = -0.5,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0.03)

>>>>

# axes_obj <- gen_axes(  
#   proj = projection * 2,
#   limits = 0.5,
#   axis_pos_x = -0.5,
#   axis_pos_y = -0.5,
#   axis_labels = names(scaled_two_curvy_data),
#   threshold = 0.03)
# 
# axes <- axes_obj$axes
# circle <- axes_obj$circle
